A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2015-01-10 ms.tex
Addressed baseline screening technique in the context of covariance based power estimation techniques and updated reference to Sutinjo et al.(2014)

The instrument model consists primarily of the tile beam power--pattern, $A(\hat{\boldsymbol{s}},f)$ (see equation~\ref{eqn:obsvis}). It is modeled as a mutually--coupled 4--by--4 dipole array with the overall power--pattern of each individual dipole calculated via finite element electromagnetic simulation \citep{sut14}. To speed up simulations, we find that a phased array of isotropic radiators at a height of 0.3~m above an infinite ground plane provides a very good approximation to the full simulation, hence we use the idealized dipoles. We also assume that each individual dipole signal has random delay fluctuations of rms 0.05~ns, a number in line with the known repeatability and stability level of the analog signal chain \citep{bow07b}. Besides having the effect of adding a time--dependent uncertainty in the power pattern, these random delay fluctuations reduce the coherence in the phased addition of dipole signals resulting in deviations from predicted models of the power--pattern, most prominently at its nulls. The power--patterns so obtained are shown in Figure~\ref{fig:power_pattern} for the pointings chosen in our study.

@@

In principle, instead of discarding selected antenna spacings altogether, we could down--weight them based on an optimal scheme. This technique provides a very simple and yet effective tool in adding a layer of control to mitigate effects of foreground contamination in EoR data analysis.

>>>>

The instrument model consists primarily of the tile beam power--pattern, $A(\hat{\boldsymbol{s}},f)$ (see equation~\ref{eqn:obsvis}). It is modeled as a mutually--coupled 4--by--4 dipole array with the overall power--pattern of each individual dipole calculated via finite element electromagnetic simulation \citep{sut14_arXiv}. To speed up simulations, we find that a phased array of isotropic radiators at a height of 0.3~m above an infinite ground plane provides a very good approximation to the full simulation, hence we use the idealized dipoles. We also assume that each individual dipole signal has random delay fluctuations of rms 0.05~ns, a number in line with the known repeatability and stability level of the analog signal chain \citep{bow07b}. Besides having the effect of adding a time--dependent uncertainty in the power pattern, these random delay fluctuations reduce the coherence in the phased addition of dipole signals resulting in deviations from predicted models of the power--pattern, most prominently at its nulls. The power--patterns so obtained are shown in Figure~\ref{fig:power_pattern} for the pointings chosen in our study.

@@

In principle, instead of discarding selected antenna spacings altogether, we could down--weight them based on an optimal scheme. For instance, the estimates of covariance computed from the delay transform bins can be naturally fed into the covariance--weighted power spectrum estimation techniques \citep{liu14a,liu14b}. It could also be used to downweight or flag contaminated baselines in imaging applications. This technique provides a very simple and yet effective tool in adding a layer of control to mitigate effects of foreground contamination in EoR data analysis.
